---
title: "STAT 390"
format: html
editor: visual
---

## Presentation 1

```{r}
#| message: false
library(tidyverse)
library(writexl)
library(janitor)
library(readxl)
library(knitr)

lms <- read_excel("/Users/meeratrivedi/Downloads/STAT 390/legal_menu_summary.xlsx")

lms %>% 
  kable()
```

### Legal Menu Option

**Redundancies**: Legal and Other Legal?

```{r}
lms %>% 
  group_by(legal_menu_option) %>% 
  summarize(sum_calls = sum(total_calls)) %>% 
  kable()
```

### Menu Selection

Why are there separate queues for the same transfer? 

- Housing >> **From Housing to Clinics** >> Clinic Voicemail Transfer
- Family >> **From Simple Divorce to Clinics** >> Clinic Voicemail Transfer
- Other Legal >> **Other Legal Issues Clinic** >> Clinic Voicemail Transfer

Is there a way to get all of these people straight to Clinic Voicemail without three separate transfer categories? Can they all be put in the same queue if they are receiving the same clinic voicemail?

**Redundancies**:

- Housing Other vs All Other Issues
- Immigration Other vs All Other Issues

```{r}
#| warning: false
lms %>% 
  filter(menu_selection != "N/A") %>% 
  group_by(legal_menu_option, menu_selection) %>% 
  summarize(sum_calls = sum(total_calls)) %>% 
  arrange(legal_menu_option, desc(sum_calls)) %>% 
  kable()
```
### Queue Selection

Is each subsequent column a different stage of the call? If so, why do people go through these same categories at multiple stages? 

- ADAPT
- Consumer
- Education
- All Subsenior Categories


```{r}
#| warning: false
lms %>% 
  filter(first_queue_name != "N/A") %>% 
  group_by(queue_selection, group_suboption) %>% 
  summarize(sum_calls = sum(total_calls)) %>%
  arrange(queue_selection, group_suboption) %>% 
  kable()
```

## Subseniors

**Redundancies**: Title switch between `group_suboption` and `first_queue_name`. 

```{r}
#| warning: false
lms %>% 
  filter(legal_menu_option == "Pre-Legal Seniors", 
         queue_selection != "ADAPT", 
         queue_selection != "N/A", 
         first_queue_name != "N/A", 
         first_queue_name != "Clinic Voicemail Transfer") %>% 
  select(queue_selection, group_suboption, first_queue_name, final_queue_name, total_calls) %>% 
  kable()
```

